Brief notes on erosion

### 2017-03-20 docs/Notes.tex
Working on interface evolution test.
Writing notes to scale curvature-driven flow differently. This is because for 2D Stokes flow, my tests show that the stress scales like 1/(L log L) instead of 1/L. This is probably because of 2D Stokes paradox type stuff.

To evolve the interface numerically, we use the $\theta$-$L$ method. Rather than re-derive the formulas, I will use the convention from Shelley 1994, with the curve parameterized in the CCW direction and the normal vector pointing {\em inward}. With this convention, the normal interface velocity is the negative of what it was previously, giving
\begin{equation}
V_n = C \atau + \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Recall that for Stokes flow, $\beta = 0$.

@@

We introduce the tangent angle $\theta$, defined by
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
so that we have
\begin{equation}
\tan \theta = y_s/x_s = y_\alpha / x_\alpha
\end{equation}
Remember the identity that $x_s^2 + y_s^2 = 1$ as this is very useful.
The curvature is given by
\begin{equation}
\kappa = x_s y_{ss} - x_{ss} y_s = \pd{\theta}{s} = L^{-1} \pd{\theta}{\alpha}
\end{equation}
We are using the standard convention, where a convex shape, like a circle, has positive curvature. The normal velocity now can be written as
\begin{equation}
V_n = C \atau + \eps L^{\beta-1} \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}

@@

@@

\subsection{Benchmark the interface evolution}
It would be good to test the interface evolution, in particular verify that the curvature-driven-flow (CDF) is 2nd order accurate in time. Initially, I thought I would be able to get exact solutions for CDF, but it turns out that the PDE (\ref{thetaEvolve}) does not reduce to simply a diffusion equation, but instead still has nonlinear terms, thus making exact solutions impractical. I also tried to recast CDF in polar coordinates for star-shapes, but still the governing PDE is not simple enough to get exact solutions. Instead, I can do a completely numerical convergence test.

>>>>

To evolve the interface numerically, we use the $\theta$-$L$ method. Rather than re-derive the formulas, I will use the convention from Shelley 1994, with the curve parameterized in the CCW direction and the normal vector pointing {\em inward}. With this convention, the normal interface velocity is the negative of what it was previously, giving
\begin{equation}
\label{Vn1}
V_n = C \atau + \eps L^{\beta} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Recall that for Stokes flow, $\beta = 0$.

@@

We introduce the tangent angle $\theta$, defined by
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
so that we have
\begin{equation}
\tan \theta = y_s/x_s = y_\alpha / x_\alpha
\end{equation}
Remember the identity that $x_s^2 + y_s^2 = 1$ as this is very useful.
The curvature is given by
\begin{equation}
\kappa = x_s y_{ss} - x_{ss} y_s = \pd{\theta}{s} = L^{-1} \pd{\theta}{\alpha}
\end{equation}
We are using the standard convention, where a convex shape, like a circle, has positive curvature. The normal velocity now can be written as
\begin{equation}
\label{Vn2}
V_n = C \atau + \eps L^{\beta-1} \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}

@@

\subsubsection{Different scaling of the stress}
Some numerical tests reveal that the stress scales like $\tau \sim 1/(L \log L)$, instead of the naive $1/L$. This might because we are in a 2D bounded domain (Stokes paradox type stuff). So we need to modify the curvature driven flow to have the same scaling. To this end, modify Eq.~(\ref{Vn1}) to read
\begin{equation}
V_n = \atau + \eps f(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
where for 2D Stokes flow, we will have $f(L) = -1/\log L$. Carrying through this change, Eq.~(\ref{Vn2}) becomes
\begin{equation}
V_n = \atau + \eps L^{-1} f(L) \left(\pd{\theta}{\alpha} - 2 \pi \right)
\end{equation}
and Eq.~(\ref{thetaEvolve}) becomes
\begin{equation}
\pd{\theta}{t} = \eps L^{-2} f(L) \ppd{\theta}{\alpha} + L^{-1} \left( \pd{\atau}{\alpha} + \pd{\theta}{\alpha} V_s \right)
\end{equation}
Then to evolve $\theta$ spectrally, we use
\begin{equation}
\td{\thh_k}{t} + 4 \pi^2 k^2 \eps L^{-2} f(L)  \thh_k = \hat{N}_k
\end{equation}

@@

\subsection{Benchmark the interface evolution}
It would be good to test the interface evolution, in particular verify that the curvature-driven-flow (CDF) is 2nd order accurate in time. Initially, I thought I would be able to get exact solutions for CDF, but it turns out that the PDE (\ref{thetaEvolve}) does not reduce to simply a diffusion equation, but instead still has nonlinear terms, thus making exact solutions impractical. I also tried to recast CDF in polar coordinates for star-shapes, but still the governing PDE is not simple enough to get exact solutions. Also, in the $\theta$-$L$ formulation I tried to determine the normal velocity to make the nonlinear terms vanish, but this does not appear possible either. Instead, I can do a completely numerical convergence test.
